Video Understanding : A review of action detection-recognition dataset

### 2024-01-12 conference_101719.tex
origin

\title{Video Understanding : A review of action detection-recognition dataset*\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Viet Hang Duong}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
hangdv@uit.edu.vn}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Duc Manh Nguyen Dang}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
22520847@gm.uit.edu.vn}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Ngoc Tram Phan Huynh}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
email address or ORCID}
}

@@

\textbf{Advancement of computer hardware} :

\begin{center}
	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
	\caption{Example of a figure caption.}
	\label{SSD300} 
\end{center}

@@

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

>>>>

\title{Video Understanding : A review of action detection-recognition dataset}

\author{\IEEEauthorblockN{1\textsuperscript{st} Viet Hang Duong}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
hangdv@uit.edu.vn}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Duc Manh Nguyen Dang}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
22520847@gm.uit.edu.vn}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Ngoc Tram Phan Huynh}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
22521500@uit.edu.vn}
}

@@

\textbf{Advancement of computer hardware} : In 1965, Gordon Moore, co-founder of Intel Corporation, made a prediction in his paper that in the next ten years, the number of transistors would double every year. Ten years later, in 1975, he revised his prediction, stating that the number of transistors would double every two years. This statement became known as Moore's Law. Although in recent years Moore's Law is no longer accurate due to technological limitations, as the size of transistors needs to decrease while their density increases, the rate of growth has been impressive. For example, in 2007, the most advanced processors like the Intel Core 2 Duo were built on a 45-nanometer process and contained approximately 230 million transistors. However, in 2023, Apple introduced the Apple A17 Pro processor, built on a 3-nanometer process with approximately 19 billion transistors, Fig.~\ref{fig1} shows the increase in the number of transistors over time. During this period, deep convolutional neural network models also made significant advancements, from models like LeNet-5 with only around 60 thousand parameters to AlexNet and VGGNet with 60 million and 138 million parameters, respectively. Moreover, in the field of natural language processing, large language models have reached parameter counts in the tens of billions. These developments have been truly impressive. It is evident that the pace of technological development has greatly contributed to the advancement of the field of artificial intelligence, where a tremendous amount of computational power is required.

\begin{center}
	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
	\caption{Example of a figure.}
	\label{fig1} 
\end{center}

\textbf{Expanding scale of datasets} : With the advancement of computer hardware and deep learning models, the demand for training datasets has also increased in terms of both the quantity of data samples and the complexity of the dataset (number of classes, contexts, etc.). Since each task has its own unique characteristics, the dataset needs to be designed specifically for each task. Additionally, similar to how computer hardware influences the field of artificial intelligence, the era of the Internet and the development of automated data collection tools have had a positive impact on the dataset construction process. As a result, over time, datasets have become more refined in terms of scale and complexity. Besides serving as training data, datasets also provide a benchmarking tool to compare the performance of different models, enabling research groups to exchange and publish research results based on consistent metrics. However, for the same task, there are not only one but many datasets collected and published by different research groups within the community. The reason for this can be attributed to authors refreshing or supplementing existing datasets or due to different perspectives on constructing datasets, leading them to propose a new one.

@@

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{figx}
\end{figure}
